---
title: "Dynamic Fit Index Cutoffs"
author: "Created by Daniel McNeish and Melissa G Wolf"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
```

### Basic Information

**Dataset:** `r  paste(input$upload$name)`

**Sample Size:** `r  paste(nrow(data()))`

**Missing Data Indicator:** `r paste(input$missing)`

```{r include=F}
if (input$Scale == "N"){
  scale<-paste("Continuous (Normal)")
  }
  if (input$Scale == "NN"){
   scale<-paste("Continuous (Non-Normal)")
  }
  if (input$Scale == "L"){
   scale<-paste("Ordinal/Likert Treated as Continuous")
  }
  if (input$Scale == "C"){
   scale<-paste("Categorical")
  }
```

**Response Scale:** `r scale`


**Estimator:** `r input$est`

```{r include=FALSE}

  if (input$Reps == 50){
  precision<-paste("Rough")
  }
  
  if (input$Reps == 100){
  precision<-paste("2-Decimal Point")
  }
  
  if (input$Reps == 250){
  precision<-paste("3-Decimal Point")
  }

if (input$Reps == 10){
  precision<-paste("Developer Test")
  }

```
**Cutoff Precision:** `r precision`

```{r include=FALSE}
if (input$Miss == "DD"){
  method<-paste("Direct Discrepancy")
}

if (input$Miss == "OP"){
  method<-paste("Omitted Paths")
}
```

**DFI Misspecification Method:** `r method`

### Path Diagram of Your Model:

```{r}
plot(PD)
```

### Your Model Fit Indices:

```{r, results='asis'}
kable(fit)
```

### Your DFI Cutoffs:

```{r, results='asis'}
kable(cutoffs)
```

### Citation Recommendations:

**To cite this software:**

Wolf, M.G. & McNeish, D. (2024). dynamic: DFI cutoffs for latent variables models
(version 2.0.0). [Software]. www.dynamicfit.app.

Wolf, M.G. & McNeish, D. (2023). dynamic: An R package for deriving dynamic fit index cutoffs for factor analysis. Multivariate Behavioral Research, 58 (1), 189-194.

**To cite the method:**

```{r, echo=FALSE, results='asis'}
ref1<-"McNeish, D. & Wolf, M.G. (2023). Dynamic fit index cutoffs for confirmatory factor analysis models. Psychological Methods, 28 (1), 61-88."
ref2<-NULL
ref3<-NULL
ref4<-NULL
ref5<-NULL

if (input$Miss == "DD"){
ref2<-"McNeish, D. & Wolf, M.G. (in press). Direct discrepancy dynamic fit index cutoffs for arbitrary covariance structure models.  Structural Equation Modeling."
}

if (input$Scale == "C"){
ref3<-"McNeish, D. (2023). Dynamic fit index cutoffs for factor analysis with Likert-type, ordinal, or binary responses. American Psychologist, 79 (9), 1061-1075."
}

if (input$Scale == "L"){
ref4<-"McNeish, D. (in press). Dynamic fit index cutoffs for treating Likert items as continuous. Psychological Methods."
}

if (input$Factors==1){
ref5<-"McNeish, D. & Wolf, M.G. (2023). Dynamic fit cutoffs for one-factor models. Behavior Research Methods, 55 (3), 1157-1174."
}

ref<-list(ref1,ref2,ref3,ref4,ref5)

ref<-ref[!unlist(lapply(ref, is.null))]

cat(unlist(ref), sep="\n\n")

```
